A Framework for Equivalence of Cast Calculi and a new Cast Representation

### 2020-10-05 paper.tex
comment

\todo[inline]{JS: say something about the difference between the above
  and what is in this paper. That's the whole point of the related work
  section from the eyes of the reviewer.}
\todo[inline]{KC: I might have some misconcept about the related work
section. You might have felt this, haha. Now I think this section is
targeting the following scenarios:
- ``I think someone has solved this problem ...''
- ``This work looks similar to paper X, what is the difference?''
- ``Is this work inspired by paper X?''
Is my understanding correct?}

>>>>

\todo[inline]{JS: say something about the difference between the above
  and what is in this paper. That's the whole point of the related
  work section from the eyes of the reviewer.}  \todo[inline]{KC: I
  might have some misconcept about the related work section. You might
  have felt this, haha. Now I think this section is targeting the
  following scenarios: - ``I think someone has solved this problem
  ...''  - ``This work looks similar to paper X, what is the
  difference?''  - ``Is this work inspired by paper X?''  Is my
  understanding correct?}  \todo[inline]{JS: yes, and make sure to
  give very explicit answers to these questions. It should feel to you
  like you're hitting the reader over the head with the most obvious
  things (to you). The above paragraph is currently insufficient
  because it doesn't emphasize what scientific constributions are new
  to our paper compared to those prior papers on coercions in normal
  form.}
